---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Launch binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jcppc/slR/main)
<!-- badges: end -->

The goal of slR package is to provide researchers with a tool to quickly build Systematic Literature Reviews outputs to include into their documents. These outputs include: data summarizarion and charts, latex tables and more....

## Installation

You can install the development version of slR from [GitHub](https://github.com/) with:

```{r installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("jcppc/slR")
```

## Setup

To properly render the charts, the **extrafont** package should be installed and fonts imported:

```{r setup, eval = FALSE}
install.packages("extrafont")
extrafont::font_import()
```

## Example

This is a basic example which shows you how to use the library:

```{r example, eval = FALSE}
# Basic example code

library(slR)

slr.file <- "/users/jcppc/slr-articles.xlsx"
authors.file <- "/users/jcppc/articles-authors.xlsx"
output.folder <- "/users/jcppc/output"

slr <-  slR::read( slr.file )
authors <-  slR::read( authors.file )

# Print the package version
slR::version()

# Latex related functions

slR::write_comments( slr, output = output.folder )
slR::write_authors( authors, output = output.folder )
slR::write_institutions( authors, output = output.folder )
slR::write_countries( authors, output = output.folder )
slR::write_continents( authors, output = output.folder )
slR::write_articles( slr, output = output.folder )
slR::write_graphics( output = output.folder )
 
# Plots related functions

slR::score_per_year_boxplot( slr, year.above = 2012, output = output.folder, save.pdf = TRUE )

```
