---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Launch binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jcppc/slR/main)
<!-- badges: end -->

The goal of **slR** package is to provide researchers with a tool to quickly build Systematic Literature Reviews outputs to include into their documents. These outputs include: data summarizarion and charts, latex tables and more....

## Installation

You can install the development version of **slR** from [GitHub](https://github.com/) with:

```{r installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("jcppc/slR")
```

## Setup

To properly render the charts, the **extrafont** package should be installed and fonts imported:

```{r setup, eval = FALSE}
install.packages("extrafont")
extrafont::font_import()
extrafont::loadfonts(device = "all", quiet = TRUE)
```

## Example

This is a basic example which shows you how to use the library:

### Step 1 - Load *Bib* file

This step is responsible to load a **bib** file with the articles you are evaluating on your **SLR** and export the metadata in two **Excel** spreadsheets for later manual completion.  

```{r example1, eval = FALSE}
# Basic example code

library(slR)

# Define the folder where to save the generated files
output.folder <- "/users/jcppc/output"

# Step 1
# If you have only a bib file with the articles, load this file
slr.file <- "/users/jcppc/slr-articles.bib"

# This function will generate two Excel files based on the data from the bib file
slr <-  slR::read( slr.file, output = output.folder )

# Files created in folder output.folder
# slr-articles.xlsx"
# slr-authors.xlsx"
```

#### Step 1.1 - Add new dimensions

This step helps you to add immediately new dimensions to the **Excel** file. These dimensions should reflect the Research Questions you are trying to answer.

**Note:** You can skip **Step 1.1** if you go directly and edit the articles **Excel** file and add new columns to it.

```{r example2, eval = FALSE}
# Add a list of new dimensions to the slr object to reflect the RQs to answer
# This needs to be done always manually because it depends on your Research Questions

dimensions <- c("Dim1","Dim2","Dim3","Dim4")
slR::add_dimensions( slr, dimensions, output = output.folder )
```


### Step 2 - Load **Excel** files

Once the **Excel** files are completed with the articles evaluation details, these files should be loaded to finish the generation of the **SLR** components (**latex** and **plot** files).

**Note:** You can skip **Step 1** if you have the articles metadata **Excel** files already created.

```{r example3, eval = FALSE}
# Step 2
# Otherwise, if you have the Excel files already created in Step 1, load them
# Once you do Step 1, you dont' need to run it anymore, because you can always start from Step 2
slr.file <- "/users/jcppc/slr-articles.xlsx"
authors.file <- "/users/jcppc/slr-authors.xlsx"

slr = list()
slr$articles <- slR::read( slr.file, output = output.folder )
slr$authors <- slR::read( authors.file, output = output.folder )
```

### Step 3 - Generate **SLR** Components

After loading the files articles and authors files, you can generate all the **SLR** components at once. You need to specify the **dimensions** for which you want to generate the components, but this parameter is *optional*.
Once generated, you should have on the folder specified in **output.folder**, multiple **latex** and **plot** files with all the statistics.

```{r example4, eval = FALSE}
slR::generate_slr_components( slr, output = output.folder, dimensions = dimensions )

# Because in this case dimensions are omitted, this function generates all default components ( except the ones dependent on the dimensions created )
# slR::generate_slr_components( slr, output = output.folder )
```

### Extras

There are multiple functions at your disposal that you can execute individually when you need to update/generate just some parts of the **SLR**.

```{r example5, eval = FALSE}
# Print the package version

slR::version()

# Latex related functions

slR::write_comments( slr, output = output.folder )
slR::write_authors( slr, output = output.folder )
slR::write_institutions( slr, output = output.folder )
slR::write_countries( slr, output = output.folder )
slR::write_continents( slr, output = output.folder )
slR::write_articles( slr, output = output.folder )
slR::write_sample_table_template( output = output.folder )
slR::write_graphics( output = output.folder )


# Plots related functions

slR::score_per_year_boxplot( slr, output = output.folder )
slR::score_per_year_barchart( slr, output = output.folder )
slR::score_per_venue_barchart( slr, output = output.folder )
slR::score_per_author_barchart( slr, output = output.folder )
slR::score_per_publication_barchart( slr, output = output.folder )
slR::author_per_year( slr, output = output.folder )
slR::publication_per_year( slr, output = output.folder )
slR::venue_per_year( slr, output = output.folder )
slR::frequency_per_continent( slr, output = output.folder )
slR::frequency_per_country( slr, output = output.folder )
slR::frequency_per_institution( slr, output = output.folder )


# Plots for each dimension
# Needs to be done for each dimension

slR::plot_dimension_frequency( slr, output = output.folder, plot.name = "plot-freq-Dim1.pdf", dimension = "Dim1" )
slR::plot_dimension_per_year( slr, output = output.folder, plot.name = "plot-Dim1.pdf", dimension = "Dim1" )
slR::plot_dimension_frequency( slr, output = output.folder, plot.name = "plot-freq-Dim2.pdf", dimension = "Dim2" )
slR::plot_dimension_per_year( slr, output = output.folder, plot.name = "plot-Dim2.pdf", dimension = "Dim2" )

# Latex tables with frequencies per dimension
# Needs to be done for each dimension

slR::write_frequency_of_dimension( slr, output = output.folder, dimension = "Dim1" )
slR::write_frequency_of_dimension( slr, output = output.folder, dimension = "Dim2" )

# Generate all latex components, including the ones related with the dimensions
# Remove parameter dimensions to skip them

slR::generate_slr_dimensions_latex( slr, output = output.folder, dimensions = dimensions )

# Generate all plot components, including the ones related with the dimensions
# Remove parameter dimensions to skip them

dimensions <- c("Dim1","Dim2","Dim3","Dim4")
slR::generate_slr_dimensions_plot( slr, output = output.folder, dimensions = dimensions )
```
